### 2025-07-11 factor-analysis.qmd
20250710 - figure labels

A path diagram of the EFA model was created using the `lavaanPlot()` function of the `lavaanPlot` package [@R-lavaanPlot].

```{r}
lavaanPlot::lavaanPlot(
  efa_fit$nf3,
  coefs = TRUE,
  stand = TRUE)
```

@@

```{r}
lavaanPlot::lavaanPlot(
  efa3factor_fit,
  coefs = TRUE,
  stand = TRUE)
```

@@

```{r}
lavaanPlot::lavaanPlot(
  efa3factorModified_fit,
  coefs = TRUE,
  stand = TRUE)
```

@@

```{r}
lavaanPlot::lavaanPlot(
  cfa1factor_fit,
  coefs = TRUE,
  stand = TRUE)
```

@@

```{r}
lavaanPlot::lavaanPlot(
  cfa2factor_fit,
  coefs = TRUE,
  stand = TRUE)
```

@@

```{r}
lavaanPlot::lavaanPlot(
  cfa3factor_fit,
  coefs = TRUE,
  stand = TRUE)
```

@@

```{r}
lavaanPlot::lavaanPlot(
  cfa3factorModified_fit,
  coefs = TRUE,
  stand = TRUE)
```

>>>>

A path diagram of the EFA model in @fig-efaPathDiagram-3factor was created using the `lavaanPlot()` function of the `lavaanPlot` package [@R-lavaanPlot].

```{r}
#| label: fig-efaPathDiagram-3factor
#| fig-cap: "Path Diagram of the Three-Factor Exploratory Factor Analysis Model."
#| fig-alt: "Path Diagram of the Three-Factor Exploratory Factor Analysis Model."

lavaanPlot::lavaanPlot(
  efa_fit$nf3,
  coefs = TRUE,
  stand = TRUE)
```

@@

A path diagram of the three-factor ESEM model is in @fig-esemPathDiagram-3factor.

```{r}
#| label: fig-esemPathDiagram-3factor
#| fig-cap: "Path Diagram of the Three-Factor Exploratory Structural Equation Model."
#| fig-alt: "Path Diagram of the Three-Factor Exploratory Structural Equation Model."

lavaanPlot::lavaanPlot(
  efa3factor_fit,
  coefs = TRUE,
  stand = TRUE)
```

@@

The path diagram of the modified ESEM model with correlated residuals is in @fig-esemPathDiagram-3factorModified.

```{r}
#| label: fig-esemPathDiagram-3factorModified
#| fig-cap: "Path Diagram of the Three-Factor Exploratory Structural Equation Model With Correlated Residuals."
#| fig-alt: "Path Diagram of the Three-Factor Exploratory Structural Equation Model With Correlated Residuals."

lavaanPlot::lavaanPlot(
  efa3factorModified_fit,
  coefs = TRUE,
  stand = TRUE)
```

@@

The path diagram of the one-factor CFA model is in @fig-cfaPathDiagram-1factor.

```{r}
#| label: fig-cfaPathDiagram-1factor
#| fig-cap: "Path Diagram of the One-Factor Confirmatory Factor Analysis Model."
#| fig-alt: "Path Diagram of the One-Factor Confirmatory Factor Analysis Model."

lavaanPlot::lavaanPlot(
  cfa1factor_fit,
  coefs = TRUE,
  stand = TRUE)
```

@@

The path diagram of the two-factor CFA model is in @fig-cfaPathDiagram-2factor.

```{r}
#| label: fig-cfaPathDiagram-2factor
#| fig-cap: "Path Diagram of the Two-Factor Confirmatory Factor Analysis Model."
#| fig-alt: "Path Diagram of the Two-Factor Confirmatory Factor Analysis Model."

lavaanPlot::lavaanPlot(
  cfa2factor_fit,
  coefs = TRUE,
  stand = TRUE)
```

@@

The path diagram of the three-factor CFA model is in @fig-cfaPathDiagram-3factor.

```{r}
#| label: fig-cfaPathDiagram-3factor
#| fig-cap: "Path Diagram of the Three-Factor Confirmatory Factor Analysis Model."
#| fig-alt: "Path Diagram of the Three-Factor Confirmatory Factor Analysis Model."

lavaanPlot::lavaanPlot(
  cfa3factor_fit,
  coefs = TRUE,
  stand = TRUE)
```

@@

The path diagram of the modified three-factor CFA model with correlated residuals is in @fig-cfaPathDiagram-3factorModified.

```{r}
#| label: fig-cfaPathDiagram-3factorModified
#| fig-cap: "Path Diagram of the Modified Three-Factor Confirmatory Factor Analysis Model With Correlated Residuals."
#| fig-alt: "Path Diagram of the Modified Three-Factor Confirmatory Factor Analysis Model With Correlated Residuals."

lavaanPlot::lavaanPlot(
  cfa3factorModified_fit,
  coefs = TRUE,
  stand = TRUE)
```
